---
title: "EDA_no_imputation"

output: html_document
---


## EDA

## Load data


```{r}
library(survey)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(VIM)
library(patchwork)
library(pROC)

nhanes_complete = read.csv("nhanes_complete_data.csv")
table(nhanes_complete$svy_year)

temp_table <- table(nhanes_complete$svy_year) %>% as.data.frame() 
colnames(temp_table) <- c("year","count")


ggplot(temp_table, aes(x=year, y=count)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=count), vjust=-0.3) + 
  labs(title="Number of observations in each survey year", x="Year", y="Count") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5,face="bold", size=10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

```




# selecting variabes
```{r}

nhanes_complete_selected_demo <- nhanes_complete[,c("SEQN",
                                      "svy_year",
                                      "svy_weight_mec",
                                      "svy_psu",
                                      "svy_strata",
                                      "DMDEDUC2",
                                      "svy_subpop_htn",
                                      "svy_subpop_chol",
                                      "DMDEDUC2",
                                      "demo_age_cat",
                                      "demo_age_years", 
                                      "demo_gender", 
                                      "demo_race", 
                                      "htn_accaha",
                                      "cc_bmi",
                                      "cc_diabetes")]


temp_vec <-nhanes_complete_selected_demo$htn_accaha %>% as.factor() %>% as.integer()
temp_vec <- temp_vec - 1
nhanes_complete_selected_demo$htn_accaha_numeric <- temp_vec %>% as.integer()

```


## Visualizing missing pattern

```{r}

aggr_plot <- aggr(nhanes_complete_selected_demo, 
                  col=c('navyblue','yellow'), 
                  numbers=TRUE, sortVars=TRUE, 
                  labels=names(data), cex.axis=.7, gap=3, 
                  ylab=c("Histogram of missing data","Pattern"))

```


```{r}

nhanes_selected <- nhanes_complete_selected_demo %>% select(-c("SEQN","svy_year","svy_weight_mec","svy_psu","svy_strata","svy_subpop_htn","svy_subpop_chol","htn_accaha_numeric","DMDEDUC2"))

missing_data<-sapply(nhanes_selected,function(x) sum(is.na(x)/length(x)))

missing_data_df <- data.frame(
  Variable = names(missing_data),
  MissingPercentage = missing_data
)


ggplot(missing_data_df, aes(x = Variable, y = MissingPercentage)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Missing Ratio", x = "Demographic Variables", y = "Ratio of Missing") +
  coord_flip()


```




## Checking variable distributions

```{r}
design <- svydesign(ids = ~svy_psu, 
                    strata = ~svy_strata, 
                    weights = ~svy_weight_mec, 
                    data = nhanes_complete_selected_demo,
                    nest = TRUE)

```



```{r}

# calculating the proportion and mean of the key covariates 

survey_year_table = svytable(~svy_year+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$svy_year %>% table() %>% rownames())
p_value = svychisq(~svy_year+htn_accaha, design)$p.value
survey_year_table = survey_year_table %>% mutate(p_value = p_value)


age_table = svytable(~demo_age_cat+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name =  nhanes_complete$demo_age_cat %>% table() %>% rownames())
p_value = svychisq(~demo_age_cat+htn_accaha, design)$p.value
age_table = age_table %>% mutate(p_value = p_value)



gender_table = svytable(~demo_gender+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble()%>% mutate(name = nhanes_complete$demo_gender %>% table() %>% rownames())
p_value = svychisq(~demo_gender+htn_accaha, design)$p.value
gender_table = gender_table %>% mutate(p_value = p_value)



race_table = svytable(~demo_race+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$demo_race %>% table() %>% rownames())
p_value =svychisq(~demo_race+htn_accaha, design)$p.value
race_table = race_table %>% mutate(p_value = p_value) 


bmi_table = svytable(~cc_bmi+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$cc_bmi %>% table() %>% rownames())
p_value =svychisq(~cc_bmi+htn_accaha, design)$p.value
bmi_table = bmi_table %>% mutate(p_value = p_value) 


diabetes_table = svytable(~cc_diabetes+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$cc_diabetes %>% table() %>% rownames()) 
p_value =svychisq(~cc_diabetes+htn_accaha, design)$p.value
diabetes_table = diabetes_table %>% mutate(p_value = p_value)


education_table = svytable(~DMDEDUC2+htn_accaha,design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$DMDEDUC2 %>% table() %>% rownames())
p_value =svychisq(~DMDEDUC2+htn_accaha,design)$p.value
education_table = education_table %>% mutate(p_value = p_value)


# design_income_complete <- subset(design,!is.na(INDFMPIR)) 
# 
# income_table = svyby(~INDFMPIR,~htn_accaha, design_income_complete,svymean) %>% as.data.frame.matrix() %>% as_tibble()
# income_table = t(income_table[,-1]) %>% as_tibble() %>% mutate(name = "Income Level")


# combinging all the tibbles vertically and write them into csv

bind_rows(list(survey_year_table,age_table,gender_table,race_table,
               bmi_table,diabetes_table,education_table)) %>% write.csv("table_one.csv")



```




## Change of Key Demo and Health variables through survey years

```{r}

# Race changes through survey years

race_table <- svytable(~demo_race+svy_year,design) %>% prop.table()
race_table <- race_table / apply(race_table,2,sum)

race_table_df <- as.data.frame(race_table)

race_year_p <- svychisq(~demo_race+svy_year,design)$p.value

race_histogram<-ggplot(race_table_df,aes(x=svy_year,y=Freq,fill=demo_race))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Race",title="Changes of Race through survey years", subtitle = paste0("Rao Scott test p value: ",round(race_year_p,4)))+
  scale_fill_brewer(palette = "Set1") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))

# Gender changes through survey years, gender variable: demo_gender

gender_table <- svytable(~demo_gender+svy_year,design) %>% prop.table()
gender_table <- gender_table / apply(gender_table,2,sum)

gender_table_df <- as.data.frame(gender_table)

gender_year_p <- svychisq(~demo_gender+svy_year,design)$p.value

gender_histogram<-ggplot(gender_table_df,aes(x=svy_year,y=Freq,fill=demo_gender))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="gender",title="Changes of gender through survey years",
       subtitle =paste0("Rao Scott test p value: ",round(gender_year_p,4)) )+
  scale_fill_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# Age changes through survey years, age variable: demo_age_cat

age_table <- svytable(~demo_age_cat+svy_year,design) %>% prop.table()
age_table <- age_table / apply(age_table,2,sum)

age_table_df <- as.data.frame(age_table)

age_year_p <- svychisq(~demo_age_cat+svy_year,design)$p.value


age_histogram<-ggplot(age_table_df,aes(x=svy_year,y=Freq,fill=demo_age_cat))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Age",title="Changes of Age through survey years",
       subtitle=paste0("Rao Scott test p value: ",round(age_year_p,4)) )+
  scale_fill_manual(values = c("pink", "green", "blue", "black")) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# BMI changes through survey years, BMI variable: cc_bmi

bmi_table <- svytable(~cc_bmi+svy_year,design) %>% prop.table()
bmi_table <- bmi_table / apply(bmi_table,2,sum)

bmi_table_df <- as.data.frame(bmi_table)

bmi_year_p <- svychisq(~cc_bmi+svy_year,design)$p.value


bmi_histogram<-ggplot(bmi_table_df,aes(x=svy_year,y=Freq,fill=cc_bmi))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="BMI",title="Changes of BMI through survey years",
       subtitle = paste0("Rao Scott test p value: ",round(bmi_year_p,4)) )+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))



# Diabetes changes through survey years, Diabetes variable: cc_diabetes

diabetes_table <- svytable(~cc_diabetes+svy_year,design) %>% prop.table()
diabetes_table <- diabetes_table / apply(diabetes_table,2,sum)

diabetes_table_df <- as.data.frame(diabetes_table)

diabetes_year_p <- svychisq(~cc_diabetes+svy_year,design)$p.value

diabetes_histogram<-ggplot(diabetes_table_df,aes(x=svy_year,y=Freq,fill=cc_diabetes))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Diabetes",title="Changes of Diabetes through survey years",subtitle= paste0("Rao Scott test p value: ",round(diabetes_year_p,4)) )+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


#library(patchwork)

combined_hist<-race_histogram+gender_histogram+
  age_histogram+
  plot_layout(ncol=1) +
  theme(plot.title = element_text(size = 14), 
                      legend.position = "bottom")

ggsave("combined_histograms.png", combined_hist, width = 8, height = 12)


```

#age, race, gender, income, survey year

## EDA analysis on People With No diet 


```{r}

nhanes_no_diet <- nhanes_complete %>% filter(bp_med_use == "No" & DRQSDIET != 1 &
                                         !is.na(DR1TKCAL) & !is.na(INDFMPIR))

nhanes_no_diet <- nhanes_no_diet[,  c("SEQN",
                                      "svy_year",
                                      "svy_weight_mec",
                                      "svy_psu",
                                      "svy_strata",
                                      "svy_subpop_htn",
                                      "svy_subpop_chol",
                                      "DMDEDUC2",
                                      "demo_age_cat",
                                      "demo_age_years", 
                                      "demo_gender", 
                                      "demo_race", 
                                      "htn_accaha",
                                      "DR1TFIBE",
                                      "DR1TCARB",
                                      "DR1TSFAT",
                                      "DR1TMFAT",
                                      "DR1TPFAT",
                                      "DR1TALCO",
                                      "cc_bmi",
                                      "cc_diabetes")] %>% mutate(sugar = DR1TCARB-DR1TFIBE,
                                                                 fatacid = DR1TMFAT+DR1TPFAT)


temp_vec <-nhanes_no_diet$htn_accaha %>% as.factor() %>% as.integer()
temp_vec <- temp_vec - 1
nhanes_no_diet$htn_accaha_numeric <- temp_vec %>% as.integer()


design_no_diet <- svydesign(ids = ~svy_psu, 
                    strata = ~svy_strata, 
                    weights = ~svy_weight_mec, 
                    data = nhanes_no_diet,
                    nest = TRUE)


temp_table <- table(nhanes_no_diet$svy_year) %>% as.data.frame() 
colnames(temp_table) <- c("year","count")


ggplot(temp_table, aes(x=year, y=count)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=count), vjust=-0.3) + 
  labs(title="Number of observations in each survey year", x="Year", y="Count") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5,face="bold", size=10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

```


```{r}

aggr_plot <- aggr(nhanes_no_diet, 
                  col=c('navyblue','yellow'), 
                  numbers=TRUE, sortVars=TRUE, 
                  labels=names(data), cex.axis=.7, gap=3, 
                  ylab=c("Histogram of missing data","Pattern"))


```



```{r}

nhanes_no_diet [,c("DR1TFIBE",
                   "DR1TCARB",
                   "DR1TSFAT",
                   "DR1TMFAT",
                   "DR1TPFAT",
                   "DR1TALCO",
                   "sugar",
                   "fatacid")] %>% summary()


```

```{r}


# Race changes through survey years

race_table <- svytable(~demo_race+svy_year,design_no_diet) %>% prop.table()
race_table <- race_table / apply(race_table,2,sum)

race_table_df <- as.data.frame(race_table)

race_year_p <- svychisq(~demo_race+svy_year,design_no_diet)$p.value

race_histogram<-ggplot(race_table_df,aes(x=svy_year,y=Freq,fill=demo_race))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Race",title="Changes of Race through survey years", subtitle = paste0("Rao Scott test p value: ",round(race_year_p,4)))+
  scale_fill_brewer(palette = "Set1") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))

# Gender changes through survey years, gender variable: demo_gender

gender_table <- svytable(~demo_gender+svy_year,design_no_diet) %>% prop.table()
gender_table <- gender_table / apply(gender_table,2,sum)

gender_table_df <- as.data.frame(gender_table)

gender_year_p <- svychisq(~demo_gender+svy_year,design_no_diet)$p.value

gender_histogram<-ggplot(gender_table_df,aes(x=svy_year,y=Freq,fill=demo_gender))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="gender",title="Changes of gender through survey years",
       subtitle =paste0("Rao Scott test p value: ",round(gender_year_p,4)) )+
  scale_fill_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# Age changes through survey years, age variable: demo_age_cat

age_table <- svytable(~demo_age_cat+svy_year,design_no_diet) %>% prop.table()
age_table <- age_table / apply(age_table,2,sum)

age_table_df <- as.data.frame(age_table)

age_year_p <- svychisq(~demo_age_cat+svy_year,design_no_diet)$p.value


age_histogram<-ggplot(age_table_df,aes(x=svy_year,y=Freq,fill=demo_age_cat))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Age",title="Changes of Age through survey years",
       subtitle=paste0("Rao Scott test p value: ",round(age_year_p,4)) )+
  scale_fill_manual(values = c("pink", "green", "blue", "black")) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


combined_hist_no_diet<-race_histogram+gender_histogram+
  age_histogram+
  plot_layout(ncol=1) +
  theme(plot.title = element_text(size = 14), 
                      legend.position = "bottom")

ggsave("combined_histograms_no_diet.png", combined_hist, width = 8, height = 12)

```

```{r}

#race

race_table_1 <- svytable(~htn_accaha+demo_race,design_no_diet) %>% prop.table()
race_table_1 <- race_table_1 / apply(race_table_1,2,sum)

race_table_df <- as.data.frame(race_table_1)

race_year_p <- svychisq(~demo_race+htn_accaha_numeric,design_no_diet)$p.value

race_histogram<-ggplot(race_table_df,aes(x=demo_race,y=Freq,fill=htn_accaha))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Race",y="Frequency",fill="Hypertention",title="Hypertention proportion grouped by Race", subtitle = paste0("Rao Scott test p value: <0.0001 "))+
  scale_fill_brewer(palette = "Set1") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))



# Gender

gender_table <- svytable(~htn_accaha+demo_gender,design_no_diet) %>% prop.table()
gender_table <- gender_table / apply(gender_table,2,sum)

gender_table_df <- as.data.frame(gender_table)

gender_year_p <- svychisq(~demo_gender+htn_accaha_numeric,design_no_diet)$p.value

gender_histogram<-ggplot(gender_table_df,aes(x=demo_gender,y=Freq,fill=htn_accaha))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Gender",y="Frequency",fill="Hypertention",title="Hypertention proportion grouped by Gender",
       subtitle =paste0("Rao Scott test p value: <0.001 "))+
  scale_fill_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


#Age Category

age_table <- svytable(~htn_accaha+demo_age_cat,design_no_diet) %>% prop.table()
age_table <- age_table / apply(age_table,2,sum)

age_table_df <- as.data.frame(age_table)

age_year_p <- svychisq(~demo_age_cat+htn_accaha_numeric,design_no_diet)$p.value


age_histogram<-ggplot(age_table_df,aes(x=demo_age_cat,y=Freq,fill=htn_accaha))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Age",y="Frequency",fill="Hypertention",title="Hypertention proportion grouped by Age",
       subtitle=paste0("Rao Scott test p value: <0.001 "))+
  scale_fill_manual(values = c("pink", "green", "blue", "black")) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# BMI : cc_bmi

bmi_table <- svytable(~htn_accaha+cc_bmi,design_no_diet) %>% prop.table()
bmi_table <- bmi_table / apply(bmi_table,2,sum)

bmi_table_df <- as.data.frame(bmi_table)

bmi_year_p <- svychisq(~cc_bmi+htn_accaha_numeric,design_no_diet)$p.value


bmi_histogram<-ggplot(bmi_table_df,aes(x=cc_bmi,y=Freq,fill=htn_accaha))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="BMI",y="Frequency",fill="Hypertention",title="Hypertention proportion grouped by BMI",
       subtitle=paste0("Rao Scott test p value: <0.001 "))+
  scale_fill_manual(values = c("pink", "green", "blue", "black")) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# Diabetes cc_diabetes

diabetes_table <- svytable(~htn_accaha+cc_diabetes,design_no_diet) %>% prop.table()
diabetes_table <- diabetes_table / apply(diabetes_table,2,sum)

diabetes_table_df <- as.data.frame(diabetes_table)

diabetes_year_p <- svychisq(~cc_diabetes+htn_accaha_numeric,design_no_diet)$p.value


diabetes_histogram<-ggplot(diabetes_table_df,aes(x=cc_diabetes,y=Freq,fill=htn_accaha))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Diabetes",y="Frequency",fill="Hypertention",title="Hypertention proportion grouped by Diabetes",
       subtitle=paste0("Rao Scott test p value: <0.001 "))+
  scale_fill_manual(values = c("pink", "green", "blue", "black")) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# Education DMDEDUC2

education_table <- svytable(~htn_accaha+DMDEDUC2,design_no_diet) %>% prop.table()
education_table <- education_table / apply(education_table,2,sum)

education_table_df <- as.data.frame(education_table)

education_year_p <- svychisq(~DMDEDUC2+htn_accaha_numeric,design_no_diet)$p.value


education_histogram<-ggplot(education_table_df,aes(x=DMDEDUC2,y=Freq,fill=htn_accaha))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Education",y="Frequency",fill="Hypertention",title="Hypertention proportion grouped by Education",
       subtitle=paste0("Rao Scott test p value: <0.001 "))+
  scale_fill_manual(values = c("pink", "green", "blue", "black")) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


combine_hitogram_no_diet <- age_histogram+race_histogram+bmi_histogram+gender_histogram+
                              diabetes_histogram+plot_layout(ncol = 2)

ggsave("combined_histograms_htn_accaha_no_diet.png", combine_hitogram_no_diet, width = 16, height = 12)


```


### Changes of macronutrient variables through survey years

#### fiber, sugar, saturated fat, unsaturated fat, alcohol




```{r}

png("macronutrient_changes.png", width = 16, height = 12, units = 'in', res = 300)

par(mfrow=c(2,2))
#fiber

box_1<-svyboxplot(DR1TFIBE~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Fiber",
           main="Changes of Fiber through survey years",
           col="lightblue",
           keep.var=TRUE,quantiles=c(0,0.25,0.5,0.75,1),ci=TRUE, na.rm = TRUE,vartype = "ci")


#sugar

box_2<-svyboxplot(sugar~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Sugar",
           main="Changes of Sugar through survey years",
           col="lightblue")

#saturated fat

box_3<-svyboxplot(DR1TSFAT~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Saturated Fat",
           main="Changes of Saturated Fat through survey years",
           col="lightblue")

#unsaturated fat

box_4<-svyboxplot(fatacid~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Unsaturated Fat",
           main="Changes of Unsaturated Fat through survey years",
           col="lightblue")

#par(OPAR)

```

.

### Difference of Macronutrients between race displayed by boxplot

```{r}

png("macronutrient_racess.png", width = 18, height = 12, units = 'in', res = 300)

par(mfrow=c(2,2))
#fiber

box_1<-svyboxplot(DR1TFIBE~demo_race,design_no_diet,
           xlab="Race",ylab="Fiber",
           main="Changes of Fiber between races",
           col="lightblue",keep.var=TRUE,quantiles=c(0,0.25,0.5,0.75,1))


#sugar

box_2<-svyboxplot(sugar~demo_race,design_no_diet,
           xlab="Race",ylab="Sugar",
           main="Changes of Sugar between races",
           col="lightblue")

#saturated fat

box_3<-svyboxplot(DR1TSFAT~demo_race,design_no_diet,
           xlab="Race",ylab="Saturated Fat",
           main="Changes of Saturated Fat between races",
           col="lightblue")

#unsaturated fat

box_4<-svyboxplot(fatacid~demo_race,design_no_diet,
           xlab="Race",ylab="Unsaturated Fat",
           main="Changes of Unsaturated Fat between races",
           col="lightblue")



```


### Difference of macronutrients among people with hypertension



```{r}

png("macronutrient_htn.png", width = 18, height = 12, units = 'in', res = 300)

par(mfrow=c(2,2))

#fiber

box_1<-svyboxplot(DR1TFIBE~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Fiber",
           main="Changes of Fiber among people with hypertension",
           col="lightblue")


#sugar

box_2<-svyboxplot(sugar~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Sugar",
           main="Changes of Sugar among people with hypertension",
           col="lightblue")


#saturated fat

box_3<-svyboxplot(DR1TSFAT~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Saturated Fat",
           main="Changes of Saturated Fat among people with hypertension",
           col="lightblue")



#unsaturated fat

box_4<-svyboxplot(fatacid~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Unsaturated Fat",
           main="Changes of Unsaturated Fat among people with hypertension",
           col="lightblue")


```

