---
title: "EDA_no_imputation"

output: html_document
---


## EDA

## Load data


```{r}
library(survey)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(VIM)
library(patchwork)
library(pROC)

nhanes_complete = read.csv("nhanes_complete_data.csv")
table(nhanes_complete$svy_year)
```




# selecting variabes
```{r}

nhanes_complete_selected_demo <- nhanes_complete[,c("SEQN",
                                      "svy_year",
                                      "svy_weight_mec",
                                      "svy_psu",
                                      "svy_strata",
                                      "svy_subpop_htn",
                                      "svy_subpop_chol",
                                      "DMDEDUC2",
                                      "demo_age_cat",
                                      "demo_age_years", 
                                      "demo_gender", 
                                      "demo_race", 
                                      "htn_accaha",
                                      "cc_bmi",
                                      "cc_diabetes")]


temp_vec <-nhanes_complete_selected_demo$htn_accaha %>% as.factor() %>% as.integer()
temp_vec <- temp_vec - 1
nhanes_complete_selected_demo$htn_accaha_numeric <- temp_vec %>% as.integer()

```


## Visualizing missing pattern

```{r}

aggr_plot <- aggr(nhanes_complete_selected_demo, 
                  col=c('navyblue','yellow'), 
                  numbers=TRUE, sortVars=TRUE, 
                  labels=names(data), cex.axis=.7, gap=3, 
                  ylab=c("Histogram of missing data","Pattern"))

```



## Checking variable distributions

```{r}
design <- svydesign(ids = ~svy_psu, 
                    strata = ~svy_strata, 
                    weights = ~svy_weight_mec, 
                    data = nhanes_complete_selected_demo,
                    nest = TRUE)

```



```{r}

# calculating the proportion and mean of the key covariates 

survey_year_table = svytable(~svy_year+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$svy_year %>% table() %>% rownames())
p_value = svychisq(~svy_year+htn_accaha, design)$p.value
survey_year_table = survey_year_table %>% mutate(p_value = p_value)


age_table = svytable(~demo_age_cat+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name =  nhanes_complete$demo_age_cat %>% table() %>% rownames())
p_value = svychisq(~demo_age_cat+htn_accaha, design)$p.value
age_table = age_table %>% mutate(p_value = p_value)



gender_table = svytable(~demo_gender+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble()%>% mutate(name = nhanes_complete$demo_gender %>% table() %>% rownames())
p_value = svychisq(~demo_gender+htn_accaha, design)$p.value
gender_table = gender_table %>% mutate(p_value = p_value)



race_table = svytable(~demo_race+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$demo_race %>% table() %>% rownames())
p_value =svychisq(~demo_race+htn_accaha, design)$p.value
race_table = race_table %>% mutate(p_value = p_value) 


bmi_table = svytable(~cc_bmi+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$cc_bmi %>% table() %>% rownames())
p_value =svychisq(~cc_bmi+htn_accaha, design)$p.value
bmi_table = bmi_table %>% mutate(p_value = p_value) 


diabetes_table = svytable(~cc_diabetes+htn_accaha, design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$cc_diabetes %>% table() %>% rownames()) 
p_value =svychisq(~cc_diabetes+htn_accaha, design)$p.value
diabetes_table = diabetes_table %>% mutate(p_value = p_value)


education_table = svytable(~DMDEDUC2+htn_accaha,design) %>% prop.table() %>% as.data.frame.matrix() %>% as_tibble() %>% mutate(name = nhanes_complete$DMDEDUC2 %>% table() %>% rownames())
p_value =svychisq(~DMDEDUC2+htn_accaha,design)$p.value
education_table = education_table %>% mutate(p_value = p_value)


# design_income_complete <- subset(design,!is.na(INDFMPIR)) 
# 
# income_table = svyby(~INDFMPIR,~htn_accaha, design_income_complete,svymean) %>% as.data.frame.matrix() %>% as_tibble()
# income_table = t(income_table[,-1]) %>% as_tibble() %>% mutate(name = "Income Level")


# combinging all the tibbles vertically and write them into csv

bind_rows(list(survey_year_table,age_table,gender_table,race_table,
               bmi_table,diabetes_table,education_table)) %>% write.csv("table_one.csv")



```




## Change of Key Demo and Health variables through survey years

```{r}

# Race changes through survey years

race_table <- svytable(~demo_race+svy_year,design) %>% prop.table()
race_table <- race_table / apply(race_table,2,sum)

race_table_df <- as.data.frame(race_table)

race_year_p <- svychisq(~demo_race+svy_year,design)$p.value

race_histogram<-ggplot(race_table_df,aes(x=svy_year,y=Freq,fill=demo_race))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Race",title="Changes of Race through survey years", subtitle = paste0("Rao Scott test p value: ",round(race_year_p,4)))+
  scale_fill_brewer(palette = "Set1") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))

# Gender changes through survey years, gender variable: demo_gender

gender_table <- svytable(~demo_gender+svy_year,design) %>% prop.table()
gender_table <- gender_table / apply(gender_table,2,sum)

gender_table_df <- as.data.frame(gender_table)

gender_year_p <- svychisq(~demo_gender+svy_year,design)$p.value

gender_histogram<-ggplot(gender_table_df,aes(x=svy_year,y=Freq,fill=demo_gender))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="gender",title="Changes of gender through survey years",
       subtitle =paste0("Rao Scott test p value: ",round(gender_year_p,4)) )+
  scale_fill_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# Age changes through survey years, age variable: demo_age_cat

age_table <- svytable(~demo_age_cat+svy_year,design) %>% prop.table()
age_table <- age_table / apply(age_table,2,sum)

age_table_df <- as.data.frame(age_table)

age_year_p <- svychisq(~demo_age_cat+svy_year,design)$p.value


age_histogram<-ggplot(age_table_df,aes(x=svy_year,y=Freq,fill=demo_age_cat))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Age",title="Changes of Age through survey years",
       subtitle=paste0("Rao Scott test p value: ",round(age_year_p,4)) )+
  scale_fill_manual(values = c("pink", "green", "blue", "black")) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


# BMI changes through survey years, BMI variable: cc_bmi

bmi_table <- svytable(~cc_bmi+svy_year,design) %>% prop.table()
bmi_table <- bmi_table / apply(bmi_table,2,sum)

bmi_table_df <- as.data.frame(bmi_table)

bmi_year_p <- svychisq(~cc_bmi+svy_year,design)$p.value


bmi_histogram<-ggplot(bmi_table_df,aes(x=svy_year,y=Freq,fill=cc_bmi))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="BMI",title="Changes of BMI through survey years",
       subtitle = paste0("Rao Scott test p value: ",round(bmi_year_p,4)) )+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))



# Diabetes changes through survey years, Diabetes variable: cc_diabetes

diabetes_table <- svytable(~cc_diabetes+svy_year,design) %>% prop.table()
diabetes_table <- diabetes_table / apply(diabetes_table,2,sum)

diabetes_table_df <- as.data.frame(diabetes_table)

diabetes_year_p <- svychisq(~cc_diabetes+svy_year,design)$p.value

diabetes_histogram<-ggplot(diabetes_table_df,aes(x=svy_year,y=Freq,fill=cc_diabetes))+
  geom_bar(stat="identity",position=position_dodge())+
  theme_minimal()+
  labs(x="Survey_year",y="Frequency",fill="Diabetes",title="Changes of Diabetes through survey years",subtitle= paste0("Rao Scott test p value: ",round(diabetes_year_p,4)) )+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5))


#library(patchwork)

combined_hist<-race_histogram+gender_histogram+
  age_histogram+bmi_histogram+diabetes_histogram+
  plot_layout(ncol=2) +
  theme(plot.title = element_text(size = 14), 
                      legend.position = "bottom")

ggsave("combined_histograms.png", combined_hist, width = 16, height = 12)


```



## Survey GLM to verify the coherence of the data merging

```{r}


model = svyglm(htn_accaha_numeric~demo_age_cat+demo_gender+demo_race+svy_year*cc_bmi+cc_diabetes,
               design,
               family=binomial)

model %>% summary() 

```

```{r}

model %>% confint()

```


```{r}

# some model diagnosis

predictions<-predict(model, type = "response")

p=mean(nhanes_complete_selected_demo$htn_accaha_numeric)

predicted_class <- ifelse(predictions > p, 1, 0) %>% unlist()



actual = nhanes_complete_selected_demo$htn_accaha_numeric [nhanes_complete_selected_demo$cc_bmi %>% is.na() %>% `!`()]

conf_matrix <- table(Predicted = predicted_class, Actual = actual)

sensitivity_value <- conf_matrix[2,2]/(conf_matrix[2,2]+conf_matrix[2,1])
specificity_value <- conf_matrix[1,1]/(conf_matrix[1,1]+conf_matrix[1,2])
accuracy_value <- (conf_matrix[1,1]+conf_matrix[2,2])/(conf_matrix[1,1]+conf_matrix[1,2]+conf_matrix[2,1]+conf_matrix[2,2])
F1_score <- 2*sensitivity_value*specificity_value/(sensitivity_value+specificity_value)


data.frame(sensitivity = sensitivity_value,
           specificity = specificity_value,
           accuracy = accuracy_value,
           F1_score = F1_score)




roc_obj <- roc(actual, predictions)

plot(roc_obj, print.thres = "best", print.thres.best.method = "closest.topleft")

auc(roc_obj)




```


## EDA analysis on People With No diet 


```{r}

nhanes_no_diet <- nhanes_complete %>% filter(bp_med_use == "No" & DRQSDIET != 1 &
                                         !is.na(DR1TKCAL) & !is.na(INDFMPIR))

nhanes_no_diet <- nhanes_no_diet[,  c("SEQN",
                                      "svy_year",
                                      "svy_weight_mec",
                                      "svy_psu",
                                      "svy_strata",
                                      "svy_subpop_htn",
                                      "svy_subpop_chol",
                                      "DMDEDUC2",
                                      "demo_age_cat",
                                      "demo_age_years", 
                                      "demo_gender", 
                                      "demo_race", 
                                      "htn_accaha",
                                      "DR1TFIBE",
                                      "DR1TCARB",
                                      "DR1TSFAT",
                                      "DR1TMFAT",
                                      "DR1TPFAT",
                                      "DR1TALCO",
                                      "cc_bmi",
                                      "cc_diabetes")] %>% mutate(sugar = DR1TCARB-DR1TFIBE,
                                                                 fatacid = DR1TMFAT+DR1TPFAT)


temp_vec <-nhanes_no_diet$htn_accaha %>% as.factor() %>% as.integer()
temp_vec <- temp_vec - 1
nhanes_no_diet$htn_accaha_numeric <- temp_vec %>% as.integer()


design_no_diet <- svydesign(ids = ~svy_psu, 
                    strata = ~svy_strata, 
                    weights = ~svy_weight_mec, 
                    data = nhanes_no_diet,
                    nest = TRUE)

```


```{r}

aggr_plot <- aggr(nhanes_no_diet, 
                  col=c('navyblue','yellow'), 
                  numbers=TRUE, sortVars=TRUE, 
                  labels=names(data), cex.axis=.7, gap=3, 
                  ylab=c("Histogram of missing data","Pattern"))


```



```{r}

nhanes_no_diet [,c("DR1TFIBE",
                   "DR1TCARB",
                   "DR1TSFAT",
                   "DR1TMFAT",
                   "DR1TPFAT",
                   "DR1TALCO",
                   "sugar",
                   "fatacid")] %>% summary()


```


### Changes of macronutrient variables through survey years

#### fiber, sugar, saturated fat, unsaturated fat, alcohol


```{r}

png("macronutrient_changes.png", width = 16, height = 12, units = 'in', res = 300)

par(mfrow=c(2,2))
#fiber

box_1<-svyboxplot(DR1TFIBE~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Fiber",
           main="Changes of Fiber through survey years",
           col="lightblue")


#sugar

box_2<-svyboxplot(sugar~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Sugar",
           main="Changes of Sugar through survey years",
           col="lightblue")

#saturated fat

box_3<-svyboxplot(DR1TSFAT~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Saturated Fat",
           main="Changes of Saturated Fat through survey years",
           col="lightblue")

#unsaturated fat

box_4<-svyboxplot(fatacid~svy_year,design_no_diet,
           xlab="Survey_year",ylab="Unsaturated Fat",
           main="Changes of Unsaturated Fat through survey years",
           col="lightblue")

```


### Difference of Macronutrients between race displayed by boxplot

```{r}

png("macronutrient_racess.png", width = 18, height = 12, units = 'in', res = 300)

par(mfrow=c(2,2))
#fiber

box_1<-svyboxplot(DR1TFIBE~demo_race,design_no_diet,
           xlab="Race",ylab="Fiber",
           main="Changes of Fiber between races",
           col="lightblue")


#sugar

box_2<-svyboxplot(sugar~demo_race,design_no_diet,
           xlab="Race",ylab="Sugar",
           main="Changes of Sugar between races",
           col="lightblue")

#saturated fat

box_3<-svyboxplot(DR1TSFAT~demo_race,design_no_diet,
           xlab="Race",ylab="Saturated Fat",
           main="Changes of Saturated Fat between races",
           col="lightblue")

#unsaturated fat

box_4<-svyboxplot(fatacid~demo_race,design_no_diet,
           xlab="Race",ylab="Unsaturated Fat",
           main="Changes of Unsaturated Fat between races",
           col="lightblue")



```


### Difference of macronutrients among people with hypertension



```{r}

png("macronutrient_htn.png", width = 18, height = 12, units = 'in', res = 300)

par(mfrow=c(2,2))

#fiber

box_1<-svyboxplot(DR1TFIBE~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Fiber",
           main="Changes of Fiber among people with hypertension",
           col="lightblue")


#sugar

box_2<-svyboxplot(sugar~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Sugar",
           main="Changes of Sugar among people with hypertension",
           col="lightblue")


#saturated fat

box_3<-svyboxplot(DR1TSFAT~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Saturated Fat",
           main="Changes of Saturated Fat among people with hypertension",
           col="lightblue")



#unsaturated fat

box_4<-svyboxplot(fatacid~htn_accaha,design_no_diet,
           xlab="Hypertension",ylab="Unsaturated Fat",
           main="Changes of Unsaturated Fat among people with hypertension",
           col="lightblue")


```


### using logistic regression to check the association between macronutrients and hypertension

```{r}
#fiber 
fiber_htn<- svyglm(htn_accaha_numeric~demo_age_cat+demo_race+demo_gender+svy_year*DR1TFIBE, design_no_diet, family = binomial) 
summary(fiber_htn)
confint(fiber_htn)
```

```{r}
#sugar
sugar_htn<-svyglm(htn_accaha_numeric~demo_age_cat+demo_race+demo_gender+svy_year*sugar, design_no_diet, family = binomial)
summary(sugar_htn)
confint(sugar_htn)
```

```{r}  
#saturated fat
satfat_htn <- svyglm(htn_accaha_numeric~demo_age_cat+demo_gender+demo_race+svy_year*DR1TSFAT, design_no_diet, family = binomial)
summary(satfat_htn)
confint(satfat_htn)
```

```{r}
#unsaturated fat
unsatfat_htn<-svyglm(htn_accaha_numeric~demo_age_cat+demo_gender+demo_race+svy_year*fatacid, design_no_diet, family = binomial)

summary(unsatfat_htn)

confint(unsatfat_htn)
```
